\chapter{FEASIBILITY STUDY}
A feasibility analysis is used to determine the viability of an idea, such as ensuring a project is legally and technically feasible as well as economically justifiable. It tells us whether a project is worth the investment—in some cases, a project may not be doable. There was research done in order to check the feasibility.
\section{Technical Feasibility}
The task focused include front end in React Js. and Flutter, backend using Flask and Node js.(when needed) and DBMS using PostgreSQL, for map Google provides there Google Maps API. All of these are chosen due to there application on various stuffs like making better design to being easily extensible and main point being open source. All of these make it feasible to apply on software level. For hardware level following are the chosen:
\subsection{PC}
Computer with following features are chosen:
\begin{enumerate}[label=(\alph*)]
	\item Processor:	Intel(R) Core(TM) i5-6200U CPU @ 2.30GHz, 2401 Mhz, 2 Core(s), 4 Logical Processor(s)
	\item Physical Memory: 4.00 GB
	\item Graphics Card: AMD Radeon (TM) R5 M330
\end{enumerate}
\subsection{Android}
Flutter Supports all the application above Android Jelly Bean 4.1.x or newer but in our case Marshmellow 6.0 is used.
\section{Economic Feasibility}
Since most of the software/program/framework being used is open source it doesn't have a big effect in the total budget of the software development. One which does require initial investment is Google's Map API which depends upon features chosen but afterwards Google gives 200\$ credit per month which enough in per month basis unless there is a overload where additional payment might be necessary. \\
Only other investment is for the labour work. All of the initial investment could be recovered though the owners sharing their rooms in our application.
\section{Time Feasibility}
Since our work flow is planned through agile model, working application can be released soon and features could be added eventually. To reach our goals, a gannt chart was developed planning the estimated time for each task. Each task were given bit more time as needed so that if needed it goal could be reached easily finishing the project on time. 
\section{Operational Feasibility}
Although due to COVID-19 pandemic physical interview could not be held but still though the mediums like Facebook, interviews were conducted. Several people pointed us to the fact that there are applications which already exists and approved on the point that most of them lacks feature we planned to include and that it would help them if they were to rent a room and would use application that is easier for them.