\pagenumbering{arabic}
\chapter{INTRODUCTION}
Home has always been a place where one’s comfort zone lies. A place where people can rest from their day-to-day stress, think about something new, have time for oneself or their family. Not all people can afford to build a house hence they go to the second option of renting a room or an apartment.

\section{Background }
 People tend to rent their place which comforts them the most i.e. people tend to rent near there work place or study place.

\section{Problem Definition}
 Finding place where one has never been to is very time consuming and even when searching might not result on finding even on empty room. Even when searching online, there is no proper way of talking to the owner in a secure manner i.e. either a site just give the phone number of the owner to the public or they just send them an email and reveal their location to the public. This has a security flaw since owners personal information is out there in public.
\section{Problem Solution}
 The solution to the problem can be seen in following ways:
 \begin{itemize}
 	\item Create an application through which owner and renter can talk with each other through the application.
 	\item Owner can approve for showing of their information if they find the request legit through chatting features in the application.
 	\item Renter can book the room after both owner and renter approves after which through google maps integration, renter can use it to find the way to owners house.
 \end{itemize}
\section{Objectives}
This work is conducted in order to: 
\begin{itemize}
  \item To make it easier for average citizen to rent a room
  \item To make it easier for average house owner to rent out a room
   
\end{itemize}