\chapter{LITERATURE REVIEW}
The main idea of this project is to make renting of rooms for average citizen easier through improving several features such as adding way of having live chat, google maps integration allowing users to use the feature of following path to reach the destination, only reveling necessary data such as rent per month, location i.e. place’s name only, Image of the place, etc. other data being shared when user allows it to be shared. \\
Various renting systems such has house renting system\cite{houserent}, car renting system projects have been done one of them being from Bangladesh, house renting system being focused on entire property similar to ‘basobas.com’. Other products such as ‘rentalnepal.com’, ‘gharbazar.com’, ‘gharbheti.com’ and even in ‘hamrobazar.com’ already exist all trying to solve their own ways. All of these have solved one problem but removing some important features from previous products i.e. Some give phone numbers only, one only allows through there emailing service, one totally lacks images of the rooms posted in the site. All of these problems were the main reason this project is viable. \\
In order for this project to go on forward Web application development, Android application development and knowledge about DBMS was necessary. For all of these, React Js., Flutter, Flask and PostgreSQL were all the technology planned to be used with the help of Object Relational Mapper Tool such as SQLAlchemy. In optional technology, Node Js. is kept so that all the planned features could be integrated even if there is any problem which may occur during backend using Flask following the Model View Controller(MVC) Architecture.
